\chapter{Aggregator}
\label{sec:aggregator}

The aggregator is the software interface
between the readers and all subsequent stages of the pipeline.
It is the first stage of the pipeline
that has total visibility of the system.
It serves two purposes at present:
\begin{itemize}
    \item It decapsulates sensor data.
    \item By using joint observations
        of tags' beacons by multiple readers,
        it estimates beacon position.
\end{itemize}

\section{Position Estimation}

The position estimation algorithm
at present
is quite simplistic,
using a sliding window average
of observations.
It assumes that reader identifiers
(IPv4 addresses)
have been mapped
to (X,Y,Z) positions in space.
Each observed beacon's reader's position
is weighted
by the inverse
of the transmission strength
noted in the beacon.
All such weighted positions
for a window worth of sequence numbers
are averaged to obtain
the present guess at position.

This technique assumes that readers well
exceed the set of plausible positions,
which is unlikely to be true.

\subsection{Area Labeling}

As a convenience,
the aggregator also maps $(X,Y,Z)$ positions
onto arbitrary labels,
which are additionally reported upstream.
This is done simply as a convenience
for upstream modules.
Currently, the lookup is done
with a binary space partition tree.

\section{Aggregator Output}

The aggregator reports
once per second
per active badge
the current timestamp,
the badge's estimated $(X,Y,Z)$ position,
the number of beacons observed in the window,
the area label,
the most recent interesting beacon ``flags'' value,
and the timestamp of that observation.
